sem

### 2023-02-09 scripts/workshop/sem.Rmd
add more models with gam

#fix error
#Error in data.frame(..., check.names = FALSE) :
#arguments imply differing number of rows: 0, 83
sem <- psem(cc_temp, size_temp, prev_cc)
sem_1 <- psem(cc_temp, size_temp, prev_temp_cc)
```

@@

@@

>>>>

#fix error
#Error in data.frame(..., check.names = FALSE) :
#arguments imply differing number of rows: 0, 83
sem_2 <- psem(cc_temp, size_temp, prev_cc)
sem_3 <- psem(cc_temp, size_temp, prev_temp_cc)
```

@@

```{r}
summary(sem_2)
```

```{r}
summary(sem_3)
```

@@

AIC
```{r}
AIC(sem, sem_1, sem_2, sem_3, sem_lagged, sem_1_lagged)
```
